Exploratory Plots

### 2023-10-18 Code/R/RMarkdown/EntropyPlots.Rmd
R code of entropies

---
title: "Exploratory Plots"
author: "Alejandro C. Frery"
date: "2023-10-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(ggthemes)
library(reshape2)
```

@@

  return(L + log(gamma(L)) + (1 - L) * digamma(L) - log(L / mu))

}
```

@@

The Shannon entropy of the GI0-SAR model is given by
\begin{multline}
H_{\mathcal{G}_I^0}(\mu, \alpha, L_0) = -\ln(\alpha)+\ln(\mu)+\ln(1+\alpha)
 -(1-\alpha)\psi^{(0)}(-\alpha) +\ln(-\alpha)-\ln L_0
+ (L_0-\alpha)\psi^{(0)}(L_0-\alpha) + \\
\ln\mathcal{B}(L_0,-\alpha)
  + (1-L_0)\psi^{(0)}(L_0), \label{E:E-GIO}
\end{multline}

>>>>

---
title: "Exploratory Plots"
author: "Alejandro C. Frery"
date: "2023-10-16"
output: pdf_document
#html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(plotly)
library(knitr)
library(rgl)
```

@@

    return(L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu))

}

entropy_gI0 <- function(mu, alpha, L) {

  term1 <- L - log(L) + log(gamma(L)) + (1 - L) * digamma(L) + log(mu)   
  term2 <- -L - log(gamma(L-alpha)) + (L-alpha)*(digamma(L - alpha))- (1-alpha)*digamma(- alpha)+log(-1 - alpha)+log(gamma(-alpha))

  entropy <- term1 + term2 
  return(entropy)
}
```

@@

The Shannon entropy of the GI0-SAR model is given by

\begin{multline}
\label{E:E-GIO}
H_{\mathcal{G}_I^0}(\mu, \alpha, L_0) =\underbrace{L_0 -\ln L_0+\ln\Gamma(L_0)+(1-L_0)\psi^{(0)}(L_0) +\ln \mu}_{H_{\Gamma_{\text{SAR}}}} 
-\ln\Gamma(L_0-\alpha)+ (L_0-\alpha) \psi^{(0)}(L_0-\alpha)\\
-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha)-L_0
\end{multline}

```{r PlotGI0, echo=FALSE}
mu <- seq(1, 10, length.out = 500)
alpha <- seq(-20, -2, length.out = 500)

entropy <- outer(mu, alpha, FUN = function(mu, alpha) entropy_gI0(mu, alpha, L = 1))

#
persp(x = mu, y = alpha, z = entropy, col = "lightblue", border = "blue")

#open3d()

#persp3d(x = mu, y = alpha,z = entropy, col = "lightblue", border = "blue")

#-----
# mu <- seq(1, 10, length.out=200)
# alpha <- seq(-2, -20, length.out=200)
# 
# 
# entropyL1 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=1))
# entropyL3 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=3))
# entropyL8 <- outer(mu, alpha,  function(mu, alpha) entropy_gI0(mu, alpha, L=8))
# entropyL12 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=12))
# entropyL100 <- outer(mu, alpha, function(mu, alpha) entropy_gI0(mu, alpha, L=100))
# 
# 
# fig <- plot_ly( x = alpha, y = mu,    showscale = FALSE)
# 
# fig <- fig %>% add_surface(z = ~entropyL1, colorscale = list(c(0,1),c("rgb(255,107,184)","rgb(128,0,64)")),  name = "L=1")
# fig <- fig %>% add_surface(z = ~entropyL3, colorscale = list(c(0,1),c("rgb(107,184,255)","rgb(90,90,124)")),  name = "L=3")
# fig <- fig %>% add_surface(z = ~entropyL8,  colorscale = list(c(0,1),c("rgb(247,226,157)","rgb(255,192,7)")),  name = "L=8")
# fig <- fig %>% add_surface(z = ~entropyL12, colorscale = list(c(0,1),c("rgb(107,255,184)","rgb(0,124,90)")),  name = "L=12")
# fig <- fig %>% add_surface(z = ~entropyL100, colorscale = list(c(0,1),c("rgb(182,142,242)","rgb(104,3,255)")),  name = "L=100")
# 
# 
# fig <- fig %>% layout(
#   scene = list(
#     xaxis = list(title = "alpha"),
#     yaxis = list(title = "mu"),
#     zaxis = list(title = "Entropy")
#   )
# )
# 
# fig
